Wide Post-Mass Transfer White-Dwarf Binaries

### 2024-07-08 summaries/june-summary.tex
reformatted paper draft, continue

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{yamaguchi-7+1.png}
    \caption{Results of how final separation $a_f$ after common envelope depends on initial separation $a_i$ for different common envelope efficiencies and energy budgets in \cite{yamaguchi_hi}.}
    \label{yam_hi}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{7+1results.png}
    \caption{COSMIC results of how final separation $a_f$ depends on initial separation $a_i$ and common envelope flag "lambdaf" for different common envelope efficiencies $\alphace$, where the black and red contour corresponds to $0.01 \au$ and $0.15 \au$ as in Figure \ref{yam_hi} respectively. Outside the black contour no desired system forms.}
    \label{res_hi}
\end{figure}
% =========================== Current Position ===========================
\subsubsection{Discussions}
Taking a closer look as the heatmap in Figure \ref{res_hi}, we notice a few interesting points.

@@

\begin{figure}
    \centering
    \includegraphics[width = 0.6\linewidth]{jump-zoom.png}
    \caption{Dependence of final separation $a_f$ on initial separation $a_i$ for $\alphace = 0.3$. Simulation results of $\lambda_f = 60$, $70$, and $80$ are shown. The red circles emphasizes the jump of final separation as initial separation increases.}
    \label{jump-zoom}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{7+1fit.png}
    \caption{Effective $\lambda$ fitting results of a $7\Msun + 1\Msun$ system for common envelope structure in MESA. \emph{Left:} MESA results in \cite{yamaguchi_hi} of how final separation $a_f$ depends on initial separation $a_i$. \emph{Center:} COSMIC results of how final separation $a_f$ depends on initial separation $a_i$, produced by the effective $\lambda$. \emph{Right:} effective $\lambda$ in COSMIC that corresponds to the MESA results for each initial separation $a_i$. The red line in the left and middle panel represents $0.15 \au$, the minimal separation for observed wide post-CE WD+MS binaries.}
    \label{fit_hi}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{7+1cmp.png}
    \caption{Same as Figure \ref{fit_hi}, but with default $\lambda$ in COSMIC model included in the right panel.}
    \label{fit_cmp_hi}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{7+1ebcmp.png}
    \caption{Same as Figure \ref{fit_cmp_hi}, but with a different energy budget.}
    \label{fit_cmp_eb_hi}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{yamaguchi-1.5+0.8.png}
    \caption{Results of how final separation $a_f$ after common envelope depends on initial separation $a_i$ for different common envelope efficiencies and energy budgets in \cite{yamaguchi_lo}. Here, for final separation $a_f <0.01\au$, WD+MS binaries are not possible, while $0.15\au$ is the observed minimal separation and $0.7\au$ is the typical separation.}
    \label{yam_lo}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{1.5+0.8results.png}
    \caption{COSMIC results of how final separation $a_f$ depends on initial separation $a_i$ and common envelope flag "lambdaf" for different common envelope efficiencies $\alphace$, where the black and red contour corresponds to $0.01 \au$, $0.15 \au$, and $0.7 \au$ as in Figure \ref{yam_lo} respectively. Outside the black contour no desired system forms since WD+MS binaries are not possible for $a_f < 0.01\au$. $0.15\au$ and $0.7\au$ are the observed minimal separation and the typical separation respectively.}
    \label{res_lo}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{1.5+0.8cmp_whole.png}
    \caption{Effective $\lambda$ fitting results of a $1.5\Msun + 0.85\Msun$ system for common envelope structure in MESA. Binding energy of the \textbf{entire envelope} is considered. \emph{Left:} MESA results in \cite{yamaguchi_lo} of how final separation $a_f$ depends on initial separation $a_i$. \emph{Center:} COSMIC results of how final separation $a_f$ depends on initial separation $a_i$, produced by the effective $\lambda$. \emph{Right:} effective $\lambda$ in COSMIC that corresponds to the MESA results for each initial separation $a_i$. The purple line represents default $\lambda$ calculated using \cite{claeys2014theoretical}. The red line and the blue line in the left and middle panel represents $0.15 \au$ and $0.7 \au$ respectively. $0.15 \au$ is the minimal separation for observed wide post-CE WD+MS binaries while $0.7 \au$ is the typical separation for such systems.}
    \label{fit_cmp_lo_whole}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{1.5+0.8cmp_pt.png}
    \caption{Same as Figure \ref{fit_cmp_lo_pt} but only binding enregy of the \textbf{outer envelope} is included.}
    \label{fit_cmp_lo_pt}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\linewidth]{stable_hi_log.png}
    \caption{COSMIC results of WD+MS binaries after stable mass transfer for $7\Msun + 1\Msun$ systems, with accretion efficiency $\beta = 0$, $\beta = 0.5$, and $\beta = 1$ respectively. \emph{Left:} dependence of final separation $a_f$ of the WD+MS binary on initial separation $a_i$. \emph{Right:} The corresponding companion mass in solar units in the WD+MS binary. The gap in both figure represents that no WD+MS system forms for that initial separation.}
    \label{stable_hi}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width = 0.75\linewidth]{stable7+1ex.png}
    \caption{COSMIC results of WD+MS binaries after stable mass transfer for two systems — $7\Msun + 0.7\Msun$ with accretion efficiency $\beta = 0.1$, and $7\Msun + 0.5\Msun$ with accretion efficiency $\beta = 0.2$. The left and right panel presents the same content as in Figure \ref{stable_hi}.}
    \label{stable_hi_ex}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{pre-spike-spike.png}
    \caption{COSMIC simulation data of $7 \Msun + 1 \Msun$ systems with accretion efficiency $\beta = 0$ and initial separation $2.30 \au$ and $2.90 \au$ respectively. They represent typical "pre-spike" binaries and "spike" binaries. The blue rectangle marks out the common first phase of evolution in both systems — contact and common envelope mass transfer.}
    \label{pre-spike-spike}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{sharp-inc-bpp.png}
    \caption{COSMIC simulation of systems $7 \Msun + 1 \Msun$ with accretion efficiency $\beta = 0$ and initial separation $2.80 \au$ and $2.90 \au$ respectively. The red rectangle emphasizes the extra mass transfer process that significantly widens the orbit without the primary losing significant mass.}
    \label{spike}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{merge-after-merge.png}
    \caption{COSMIC simulation of systems $7 \Msun + 1 \Msun$ with accretion efficiency $\beta = 0$ and initial separation $3.25 \au$ and $5.00 \au$ respectively. The blue rectangle emphasizes the differences of two evolution process, which also represents the typical difference between \textbf{merge} and \textbf{after-merge} systems.}
    \label{merge-after-merge}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{theory-observed.png}
    \caption{$M_{\mathrm{WD}} - P_{\mathrm{orb}}$ relation of observed wide post-mass transfer binaries. Binaries going through stable mass transfer is expected to fall in the grey region, as calculated in \cite{rappaport1995relation}.}
    \label{theory-observed}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{sample-distribution.png}
	\caption{The distribution of primary mass, companion mass, and orbital period in the sampled population using independent sampler. \emph{Left:} Distribution of primary mass and companion mass in log scale. \emph{Right:} Distribution of orbital period $\Porb$ in log scale.}
	\label{sample-distribution}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{Mwd-P scatter.png}
	\caption{Scatter plot of white dwarf mass $\MWD$ and final orbital period after common envelope in log scale $\log_{10}\Porb$. Different colors indicates results for different $\lambda$ values. For each different $\lambda$ value the same initial population is used.}
	\label{Mwd-P-scatter}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{kstar-map-rearr.png}
	\caption{Each panel: for this $\lambda$ value, scatter plot of white dwarf mass $\MWD$ and final orbital period after common envelope in log scale $\log_{10}\Porb$. Different colors represent different kstar type of the primary at the start of mass transfer.}
	\label{kstar-map}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{dif-kstar map.png}
	\caption{Scatter plot of difference in orbital period $\Delta P = P_{\mathrm{orb}}^{\lambda = 35} - P_{\mathrm{orb}}^{\lambda = 5}$ against the white dwarf mass $\MWD$. Different colors indicates different kstar type of the primary at the start of mass transfer.}
	\label{dif-kstar map}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{dif-kstar two plot.png}
	\caption{Left panel: scatter plot of initial orbital period at the start of RLOF $P_{\mathrm{orb}, i}$ against the final white dwarf mass $\MWD$. The color of the dots indicates how the final orbital period $P_{\mathrm{orb}, f}$ changes with respect to $\lambda=35$ and $\lambda=5$. That is, the color indicates the magnitude of $\Delta P = P_{\mathrm{orb}}^{\lambda = 35} - P_{\mathrm{orb}}^{\lambda = 5}$. Right panel: scatter plot of $\log_{10} \Delta \Porb$ against the initial orbital period in log scale $\log_{10} P_{\mathrm{orb}, i}$ at the start of RLOF. Different colors indicates different kstar type of the primary at the start of RLOF.}
	\label{dif-kstar-exp}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig/yamaguchi-7+1.png}
    \caption{Results of how final separation $a_f$ after common envelope depends on initial separation $a_i$ for different common envelope efficiencies and energy budgets in \cite{yamaguchi_hi}.}
    \label{yam_hi}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{fig/7+1results.png}
    \caption{COSMIC results of how final separation $a_f$ depends on initial separation $a_i$ and common envelope flag "lambdaf" for different common envelope efficiencies $\alphace$, where the black and red contour corresponds to $0.01 \au$ and $0.15 \au$ as in Figure \ref{yam_hi} respectively. Outside the black contour no desired system forms.}
    \label{res_hi}
\end{figure}
% =========================== Current Position ===========================
\subsubsection{Discussions}
Taking a closer look as the heatmap in Figure \ref{res_hi}, we notice a few interesting points.

@@

\begin{figure}
    \centering
    \includegraphics[width = 0.6\linewidth]{fig/jump-zoom.png}
    \caption{Dependence of final separation $a_f$ on initial separation $a_i$ for $\alphace = 0.3$. Simulation results of $\lambda_f = 60$, $70$, and $80$ are shown. The red circles emphasizes the jump of final separation as initial separation increases.}
    \label{jump-zoom}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{fig/7+1fit.png}
    \caption{Effective $\lambda$ fitting results of a $7\Msun + 1\Msun$ system for common envelope structure in MESA. \emph{Left:} MESA results in \cite{yamaguchi_hi} of how final separation $a_f$ depends on initial separation $a_i$. \emph{Center:} COSMIC results of how final separation $a_f$ depends on initial separation $a_i$, produced by the effective $\lambda$. \emph{Right:} effective $\lambda$ in COSMIC that corresponds to the MESA results for each initial separation $a_i$. The red line in the left and middle panel represents $0.15 \au$, the minimal separation for observed wide post-CE WD+MS binaries.}
    \label{fit_hi}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig/7+1cmp.png}
    \caption{Same as Figure \ref{fit_hi}, but with default $\lambda$ in COSMIC model included in the right panel.}
    \label{fit_cmp_hi}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig/7+1ebcmp.png}
    \caption{Same as Figure \ref{fit_cmp_hi}, but with a different energy budget.}
    \label{fit_cmp_eb_hi}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig/yamaguchi-1.5+0.8.png}
    \caption{Results of how final separation $a_f$ after common envelope depends on initial separation $a_i$ for different common envelope efficiencies and energy budgets in \cite{yamaguchi_lo}. Here, for final separation $a_f <0.01\au$, WD+MS binaries are not possible, while $0.15\au$ is the observed minimal separation and $0.7\au$ is the typical separation.}
    \label{yam_lo}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{fig/1.5+0.8results.png}
    \caption{COSMIC results of how final separation $a_f$ depends on initial separation $a_i$ and common envelope flag "lambdaf" for different common envelope efficiencies $\alphace$, where the black and red contour corresponds to $0.01 \au$, $0.15 \au$, and $0.7 \au$ as in Figure \ref{yam_lo} respectively. Outside the black contour no desired system forms since WD+MS binaries are not possible for $a_f < 0.01\au$. $0.15\au$ and $0.7\au$ are the observed minimal separation and the typical separation respectively.}
    \label{res_lo}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig/1.5+0.8cmp_whole.png}
    \caption{Effective $\lambda$ fitting results of a $1.5\Msun + 0.85\Msun$ system for common envelope structure in MESA. Binding energy of the \textbf{entire envelope} is considered. \emph{Left:} MESA results in \cite{yamaguchi_lo} of how final separation $a_f$ depends on initial separation $a_i$. \emph{Center:} COSMIC results of how final separation $a_f$ depends on initial separation $a_i$, produced by the effective $\lambda$. \emph{Right:} effective $\lambda$ in COSMIC that corresponds to the MESA results for each initial separation $a_i$. The purple line represents default $\lambda$ calculated using \cite{claeys2014theoretical}. The red line and the blue line in the left and middle panel represents $0.15 \au$ and $0.7 \au$ respectively. $0.15 \au$ is the minimal separation for observed wide post-CE WD+MS binaries while $0.7 \au$ is the typical separation for such systems.}
    \label{fit_cmp_lo_whole}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig/1.5+0.8cmp_pt.png}
    \caption{Same as Figure \ref{fit_cmp_lo_pt} but only binding enregy of the \textbf{outer envelope} is included.}
    \label{fit_cmp_lo_pt}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\linewidth]{fig/stable_hi_log.png}
    \caption{COSMIC results of WD+MS binaries after stable mass transfer for $7\Msun + 1\Msun$ systems, with accretion efficiency $\beta = 0$, $\beta = 0.5$, and $\beta = 1$ respectively. \emph{Left:} dependence of final separation $a_f$ of the WD+MS binary on initial separation $a_i$. \emph{Right:} The corresponding companion mass in solar units in the WD+MS binary. The gap in both figure represents that no WD+MS system forms for that initial separation.}
    \label{stable_hi}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width = 0.75\linewidth]{fig/stable7+1ex.png}
    \caption{COSMIC results of WD+MS binaries after stable mass transfer for two systems — $7\Msun + 0.7\Msun$ with accretion efficiency $\beta = 0.1$, and $7\Msun + 0.5\Msun$ with accretion efficiency $\beta = 0.2$. The left and right panel presents the same content as in Figure \ref{stable_hi}.}
    \label{stable_hi_ex}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig/pre-spike-spike.png}
    \caption{COSMIC simulation data of $7 \Msun + 1 \Msun$ systems with accretion efficiency $\beta = 0$ and initial separation $2.30 \au$ and $2.90 \au$ respectively. They represent typical "pre-spike" binaries and "spike" binaries. The blue rectangle marks out the common first phase of evolution in both systems — contact and common envelope mass transfer.}
    \label{pre-spike-spike}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig/sharp-inc-bpp.png}
    \caption{COSMIC simulation of systems $7 \Msun + 1 \Msun$ with accretion efficiency $\beta = 0$ and initial separation $2.80 \au$ and $2.90 \au$ respectively. The red rectangle emphasizes the extra mass transfer process that significantly widens the orbit without the primary losing significant mass.}
    \label{spike}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig/merge-after-merge.png}
    \caption{COSMIC simulation of systems $7 \Msun + 1 \Msun$ with accretion efficiency $\beta = 0$ and initial separation $3.25 \au$ and $5.00 \au$ respectively. The blue rectangle emphasizes the differences of two evolution process, which also represents the typical difference between \textbf{merge} and \textbf{after-merge} systems.}
    \label{merge-after-merge}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig/theory-observed.png}
    \caption{$M_{\mathrm{WD}} - P_{\mathrm{orb}}$ relation of observed wide post-mass transfer binaries. Binaries going through stable mass transfer is expected to fall in the grey region, as calculated in \cite{rappaport1995relation}.}
    \label{theory-observed}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/sample-distribution.png}
	\caption{The distribution of primary mass, companion mass, and orbital period in the sampled population using independent sampler. \emph{Left:} Distribution of primary mass and companion mass in log scale. \emph{Right:} Distribution of orbital period $\Porb$ in log scale.}
	\label{sample-distribution}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{fig/Mwd-P scatter.png}
	\caption{Scatter plot of white dwarf mass $\MWD$ and final orbital period after common envelope in log scale $\log_{10}\Porb$. Different colors indicates results for different $\lambda$ values. For each different $\lambda$ value the same initial population is used.}
	\label{Mwd-P-scatter}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/kstar-map-rearr.png}
	\caption{Each panel: for this $\lambda$ value, scatter plot of white dwarf mass $\MWD$ and final orbital period after common envelope in log scale $\log_{10}\Porb$. Different colors represent different kstar type of the primary at the start of mass transfer.}
	\label{kstar-map}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{fig/dif-kstar map.png}
	\caption{Scatter plot of difference in orbital period $\Delta P = P_{\mathrm{orb}}^{\lambda = 35} - P_{\mathrm{orb}}^{\lambda = 5}$ against the white dwarf mass $\MWD$. Different colors indicates different kstar type of the primary at the start of mass transfer.}
	\label{dif-kstar map}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/dif-kstar two plot.png}
	\caption{Left panel: scatter plot of initial orbital period at the start of RLOF $P_{\mathrm{orb}, i}$ against the final white dwarf mass $\MWD$. The color of the dots indicates how the final orbital period $P_{\mathrm{orb}, f}$ changes with respect to $\lambda=35$ and $\lambda=5$. That is, the color indicates the magnitude of $\Delta P = P_{\mathrm{orb}}^{\lambda = 35} - P_{\mathrm{orb}}^{\lambda = 5}$. Right panel: scatter plot of $\log_{10} \Delta \Porb$ against the initial orbital period in log scale $\log_{10} P_{\mathrm{orb}, i}$ at the start of RLOF. Different colors indicates different kstar type of the primary at the start of RLOF.}
	\label{dif-kstar-exp}
\end{figure}

### 2024-07-08 summaries/paper-draft-plain.tex
reformatted paper draft, continue

\documentclass[linenumbers]{aastex631}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\Msun}{\mathrm{M_{\odot}}}
\newcommand{\Rsun}{\mathrm{R_{\odot}}}
\newcommand{\MWD}{M_{\mathrm{WD}}}
\newcommand{\Mstar}{M_{\star}}
\newcommand{\alphace}{\alpha_{\mathrm{CE}}}
\newcommand{\alphath}{\alpha_{\mathrm{th}}}
\newcommand{\alpharec}{\alpha_{\mathrm{rec}}}
\newcommand{\Ebind}{E_{\mathrm{bind}}}
\newcommand{\Egrav}{E_{\mathrm{grav}}}
\newcommand{\Eint}{E_{\mathrm{int}}}
\newcommand{\Eth}{E_{\mathrm{th}}}
\newcommand{\Erec}{E_{\mathrm{rec}}}
\newcommand{\Porb}{P_{\mathrm{orb}}}
\newcommand{\au}{\, \mathrm{au}}

@@

\title{Wide Post-Mass Transfer White Dwarf Binaries}

%\author[0000-0002-0786-7307]{Greg J. Schwarz}
%\affiliation{American Astronomical Society \\
%1667 K Street NW, Suite 800 \\
%Washington, DC 20006, USA}

\author{Runqiu Ye}
\affiliation{Carnegie Mellon University}

%\collaboration{20}{(AAS Journals Data Editors)}
%
%\author{F.X Timmes}
%\affiliation{Arizona State University}
%\affiliation{AAS Journals Associate Editor-in-Chief}
%
%\author{Amy Hendrickson}
%\altaffiliation{AASTeX v6+ programmer}
%\affiliation{TeXnology Inc.}
%
%\author{Julie Steffen}
%\affiliation{AAS Director of Publishing}
%\affiliation{American Astronomical Society \\
%1667 K Street NW, Suite 800 \\
%Washington, DC 20006, USA}

\begin{abstract}

(***TO-DO***) This example manuscript is intended to serve as a tutorial and template for
authors to use when writing their own AAS Journal articles. The manuscript
includes a history of \aastex\ and includes figure and table examples to illustrate these features. Information on features not explicitly mentioned in the article can be viewed in the manuscript comments or more extensive online
documentation. Authors are welcome replace the text, tables, figures, and
bibliography with their own and submit the resulting manuscript to the AAS
Journals peer review system.  The first lesson in the tutorial is to remind
authors that the AAS Journals, the Astrophysical Journal (ApJ), the
Astrophysical Journal Letters (ApJL), the Astronomical Journal (AJ), and
the Planetary Science Journal (PSJ) all have a 250 word limit for the 
abstract\footnote{Abstracts for Research Notes of the American Astronomical 
Society (RNAAS) are limited to 150 words}.  If you exceed this length the
Editorial office will ask you to shorten it. This abstract has 161 words.

\end{abstract}

\keywords{(***TO-DO***) Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of astronomy(1868) --- Interdisciplinary astronomy(804)}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{7+1results.png}
	\caption{ Heat map of final separation $a_f$ against initial separation $a_i$ and CE flag lambdaf$=-\lambda$. Different panels represent four different CE efficiencies $\alphace = 1$, $0.9$, $0.6$, and $0.3$. The white and yellow contour corresponds to $a_f = 0.01 \au$ and $a_f = 0.15 \au$ respectively. WD+MS binaries is not possible for separation smaller than $0.01 \au$, and $0.15 \au$ is the minimum separation of wide WD+MS binaries in observational results. Outside the white contour no desired system forms.}
	\label{res_hi}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width = 0.5\linewidth]{jump-zoom.png}
	\caption{Dependence of final separation $a_f$ on initial separation $a_i$ for $\alphace = 0.3$. Simulation results of $\lambda_f = 60$, $70$, and $80$ are shown. The red circles emphasizes the jump of final separation as initial separation increases.}
	\label{jump-zoom}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{7+1fit.png}
	\caption{Effective $\lambda$ fitting results of a $7\Msun + 1\Msun$ system for common envelope structure in MESA. Left panel: MESA results in \cite{yamaguchi_hi} of how final separation $a_f$ depends on initial separation $a_i$. Central panel: COSMIC results of how final separation $a_f$ depends on initial separation $a_i$, produced by the effective $\lambda$ calculated. Right panel: effective $\lambda$ in COSMIC that corresponds to the MESA results for each initial separation $a_i$. The red dashed line in the left and middle panel represents $0.15 \au$, which is the minimal separation for observed wide post-CE WD+MS binaries.}
	\label{fit_hi}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{7+1cmp.png}
	\caption{Same as Figure \ref{fit_hi}, but with default $\lambda$ in COSMIC model included in the right panel.}
	\label{fit_cmp_hi}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{7+1ebcmp.png}
	\caption{Same as Figure \ref{fit_cmp_hi}, but with a different energy budget — $\Ebind = \Egrav + \alphath \Eth + \alpharec \Erec$.}
	\label{fit_cmp_eb_hi}
\end{figure}

@@

\bibliography{reference.bib}
\bibliographystyle{aasjournal}

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[top=0.60in, bottom=0.80in, left=0.60in, right=0.60in]{geometry}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{listings}

\newcommand{\Msun}{\mathrm{M_{\odot}}}
\newcommand{\Rsun}{\mathrm{R_{\odot}}}
\newcommand{\MWD}{M_{\mathrm{WD}}}
\newcommand{\Mstar}{M_{\star}}
\newcommand{\alphace}{\alpha_{\mathrm{CE}}}
\newcommand{\alphath}{\alpha_{\mathrm{th}}}
\newcommand{\alpharec}{\alpha_{\mathrm{rec}}}
\newcommand{\Ebind}{E_{\mathrm{bind}}}
\newcommand{\Egrav}{E_{\mathrm{grav}}}
\newcommand{\Eint}{E_{\mathrm{int}}}
\newcommand{\Eth}{E_{\mathrm{th}}}
\newcommand{\Erec}{E_{\mathrm{rec}}}
\newcommand{\Porb}{P_{\mathrm{orb}}}
\newcommand{\au}{\, \mathrm{au}}

\title{Wide Post-Mass Transfer White-Dwarf Binaries}
\author{Runqiu Ye}
\date{June, 2024}

@@

\maketitle

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{fig/7+1results.png}
  \caption{ Heat map of final separation $a_f$ against initial separation $a_i$ and CE flag lambdaf$=-\lambda$. Different panels represent four different CE efficiencies $\alphace = 1$, $0.9$, $0.6$, and $0.3$. The white and yellow contour corresponds to $a_f = 0.01 \au$ and $a_f = 0.15 \au$ respectively. WD+MS binaries is not possible for separation smaller than $0.01 \au$, and $0.15 \au$ is the minimum separation of wide WD+MS binaries in observational results. Outside the white contour no desired system forms.}
  \label{res_hi}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width = 0.5\linewidth]{fig/jump-zoom.png}
  \caption{Dependence of final separation $a_f$ on initial separation $a_i$ for $\alphace = 0.3$. Simulation results of $\lambda_f = 60$, $70$, and $80$ are shown. The red circles emphasizes the jump of final separation as initial separation increases.}
  \label{jump-zoom}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/7+1fit.png}
  \caption{Effective $\lambda$ fitting results of a $7\Msun + 1\Msun$ system for common envelope structure in MESA. Left panel: MESA results in \cite{yamaguchi_hi} of how final separation $a_f$ depends on initial separation $a_i$. Central panel: COSMIC results of how final separation $a_f$ depends on initial separation $a_i$, produced by the effective $\lambda$ calculated. Right panel: effective $\lambda$ in COSMIC that corresponds to the MESA results for each initial separation $a_i$. The red dashed line in the left and middle panel represents $0.15 \au$, which is the minimal separation for observed wide post-CE WD+MS binaries.}
  \label{fit_hi}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/7+1cmp.png}
  \caption{Same as Figure \ref{fit_hi}, but with default $\lambda$ in COSMIC model included in the right panel.}
  \label{fit_cmp_hi}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/7+1ebcmp.png}
  \caption{Same as Figure \ref{fit_cmp_hi}, but with a different energy budget — $\Ebind = \Egrav + \alphath \Eth + \alpharec \Erec$.}
  \label{fit_cmp_eb_hi}
\end{figure}

@@

\bibliography{reference.bib}
\bibliographystyle{apalike}
